Learning Actionable Analytics (with applications for reducing defects and reducing runtimes)

### 2015-05-05 how.tex
Updates from ShareLaTeX

Also, even when there is an existing model, instance-based reasoning can be useful.
Models need maintenance lest they become out-dated. Elsewhere, we have described our
extensions to the USC models to enable reasoning about agile software developments. 
It took many months to implement and certify those extensions~\cite{me09i,me09j}.
The problem of model maintenance is another
motivation to look for alternate methods that can be automateically updated whenever new data arrives.

@@

For HOW v1.0 (reported in this paper), we committed to a policy
of {\em minimal displacement}  since we do not wish to alarm developers and managers
with large scale change requests.
Note that minimal displacement makes HOW very different
to evolutionary optimizers.
Those algorithms, which include  
GALE, NSGA-II, NSGA-III, SPEA2, IBEA, PSO, DE and  MOEA/D~\cite{krall14,deb00a,zit02,zit04,%
deb14,Cui2005a,storn97,zhang07:TEC} can make large scale
displacements to the original population.

Accordingly, HOW v1.0  executes by:
\be
\item Dividing the $N$ training examples into many small clusters (each of size of , at most, $\sqrt{N}$);
\item
For a test instance that falls into cluster $C_i$,
never displace more than the boundary of that  cluster.
\ee
For the purposes of clustering, we use the WHERE recursive
descent procedure~\cite{me
WHERE is a spectral clusterer; i.e. it
executes over   synthesized dimensions discovered
by a 
principle components analysis (PCA)

Having  limiting the displacement {\em distance} to within one cluster,
there is still the issue of how to select the displacement 
{\em direction}.

Let the training and test instances comprise pair of independent and objective values. For example:
\bi 
\item
For the Seigmund data,
the objective score is the runtime of the test suite of some compiled program;
\item
For the Jureczko data, the objective score
is a boolean that is true if defects have been noted
for that class.
\ei
Let $X,Y$ be particular  training and test instance.
Further, 
let the training data be clustered and $X$
comes from a cluster $C_i$ that is near the test instance $Y$
and has objective scores better than those seen in $Y$.
We call $X$  the {\em exemplar} of $C_i$ since it
holds independent values that best characterize that cluster:
\bi
\item
For
instances with numeric objectives (e.g. the Seigmund data), 
the exemplar of a cluster is the instance
with the best objective score.
\item
For instances with discrete objectives (e.g. Jureczko data),
there is less differentiation between the objective scores.
Hence, for this kind of the data, the exemplar of a cluster is
an instance synthesized from the median values of the instances
in that cluster.
\ei
Given the above, we can now define a {\em plan} to be
a set of values to be added to a test instance in order
to reduce the distance between that instance and the exemplar: 
\[Y_j = Y_j + f*(X_j - Y_j)\]
In the above, $Y_j$ is an independent variable within the
test instance $Y$; $X$ is the exemplar found at training time;
and  $f$ is a constant that controls
how far we  move an instance (which is tuned for different data
sets).

A core design principle for HOW was ``minimal change'';
i.e. make very small changes to the current instance.
\ei
There are many ways to find those regions 
When designing HOW, our premises were:
\bi
\item
This is no domain model; (b)~we have some
labelled data and (b)~we seek minimal
disrupttion
HOW divide training into regions where the training
data has similar properties. Each region is then examined and divided into ``west'' and ``east''
where the region's ``west'' end has examples with worst performance stores than the east
end (mnemoc: west starts with ``w'' and is short for ``worst' and east starts with ``e;;]which is shirt
for excellent).so the ``e'' in

@@

For the  Jureczko   object-oriented data,
the plans generated by HOW advise   how to change static code attributes in order to reduce defects in
Java classes.  Here,
performance can be measured in terms of recall (percent of faulty classes in
the test data detected
by the {\em predictor}). Using engineering judgement, we define satisfactory recall as anything over   70\%. 
This paper explores 12 of the Jureczko   object-oriented static code data sets: Ant, Camel, Ivy, Jedit, JBeans, Log4, Lucene, Poi, Synapse, Velocity, Xalan, Xerces\footnote{Available from the object-oriented defects section of the PROMISE respository openscience.us/repo/defect/ck.}.
For each of these data sets, we generated  {\em before} scores  by finding the latest
version $k$, then training  a predictor on versions $k-2$ and $k-1$. As reported below,
our initial recall scores from this data were unpromising (very low recall values). However,
after applying certain data pre-processing steps (described below), a Random Forest generated
on the $k-2,k-1$ versions achieved recalls on version $k$ of
%issue24
\[\mathrm{recall}=\{98,88,86,84,82,81,79,78,78,\overbrace{55,23,20}^{\mathrm{JBeans,Poi,Xalan}}\}\]
From the above, we conclude that all the Seigmund configuration data and most of the Jureczko data
avoids the problem of poor predictors. Hence, we can use that data for the planning
experiments described below.

@@

We reason that the most informative feature must undergo a larger change as compared to other features. Therefore, when feature weighting is employed, the higher ranked features are mutated by a larger extent. Additionally, we have also included information pruning. Here we mutate only the top X\% of the features in each test instance. The remaining features remain unaltered. 
\begin{figure}[htbp!]
\small
\begin{tabular}{|p{.95\linewidth}|}\hline
HERE begins by \textit{clustering} the training data into similar subsets using WHERE. WHERE works as follows:
\begin{enumerate}
\item Find the two most dist points in a given population; say {\em east} and {\em west}. 
\item Draw an axis of length $c$ between the poles. 
\item Let each point be at distance $a,b$ to the {\em east,west} poles.  Using the cosine rule, project each point onto the  axis  at $x=(a^2 + c^2 - b^2)/(2c)$.  
\item Using the Median $x$ value, divide the population.
\item For each half that is larger than $\sqrt{N}$ of the original population, go to step 1.
\end{enumerate}

There are couple of things to note: firstly, the above algorithm requires a distance measure between sets of decisions, for this WHERE uses case-based reasoning measure defined by Aha et al.~\cite{aha91}; secondly, in step-1 a linear time heuristic called FASTMAP~\cite{fastmap} is used to find the two most dist points, this procedure is listed below:
\begin{itemize}
\item Pick a point at random; 
\item Let {\em east} be the point furthest from that point; 
\item Then {\em west} be the point furthest from {\em east}.
\end{itemize}

The final clusters that are found by WHERE are then used by HERE as follows:
\begin{itemize}
\item For each cluster find its nearest neighbor.
\item Construct a projective plane for each cluster pair. Label the cluster pairs as {\em Good} and {\em Bad}.
\item For a test instance, project it onto the planes generated above and pick the one on which the test case has the largest projection.
\item Mutate the attributes of the test case towards the {\em Good Cluster} in that projective plane. 
\end{itemize}

Formally, HERE can be considered as an instance based  learning scheme. And that's because it builds a set of recommendations based on a given test case based on the clusters for Median at the training stage. This is unlike a model based approach, which would have used a model to do the same~\cite{xomo}.
\\\hline
\end{tabular}
\caption{Inside HERE}\label{fig:what}
\end{figure}

>>>>

Also, even when there is an existing model, instance-based reasoning can be useful.
Models need maintenance lest they become out-dated. Elsewhere, we have described our
extensions to the USC models to enable reasoning about agile software developments. 
It took many months to implement and certify those extensions~\cite{me09i,me09j}.
The problem of model maintenance is another
motivation to look for alternate methods that can be automatically updated whenever new data arrives.

@@

For HOW v1.0 (reported in this paper), we committed to a policy
of {\em minimal displacement}  since we do not wish to alarm developers and managers
with large scale change requests.
HOW's minimal displacement policy is to generate
many small clusters, then limit displacement to the distance
to the nearest cluster.
Note that minimal displacement makes HOW very different
to evolutionary optimizers.
Those algorithms, which include  
GALE, NSGA-II, NSGA-III, SPEA2, IBEA, PSO, DE and  MOEA/D~\cite{krall14,deb00a,zit02,zit04,%
deb14,Cui2005a,storn97,zhang07:TEC} can make large scale
displacements to the original population.

For the purposes of clustering, we use the WHERE recursive
descent procedure of \fig{where} that converts
$N$ instances into $\sqrt{N}$ clusters.
WHERE is a spectral clusterer~\cite{kamvar03}; i.e. it
executes in near linear time to generate
cluster using dimensions  discovered
by a  PCA-like analysis (PCA=principle components analysis).

\begin{figure}[t!]
\small
\begin{tabular}{|p{.95\linewidth}|}\hline
WHERE recursive divides data as follows.
It finds the two   distance instances,  $X,Y$
by picking any instance $W$ at random, then setting $X$ to its most
distant instance, then setting $Y$ to the instance most distant from
$X$. 
Note that finding $X,Y$ requires only $O(2N)$ comparisons
of $N$ instances.

Let $c=dist(X,Y)$. Using $c$, we next  project each instance $Z$
onto a line that  runs between $X,Y$ as follows. If $a=dist(Z,X)$ and
$b=dist(Z,Y)$, the $Z$'s
distance from   {\em X} along the $XY$ line is
$x=(a^2 + c^2 - b^2)/(2c)$.
To recurse, split the data at the median $x$ value of all instances then call WHERE on each half (stopping when
one half has less  than $\sqrt{N}$ of the original population

In the above, to computer distances, we use
the Euclidean measure recommended for
instance-based reasoning by Aha et al.~\cite{aha91};
i.e. $\sqrt{\sum_i(X_i-Y_i)^2}$ where $X_i,Y_i$
are values normalized 0..1 for the range min..max.
\\\hline
\end{tabular}
\caption{Clustering data with WHERE. From~\cite{me12d}.}\label{fig:where}
\end{figure}

Having  limiting the displacement {\em distance} to no further that
the nearest  cluster,
there is still the issue of how to select the displacement 
{\em direction}. 
To determine that direction, we reflect on the objective
scores of each cluster.
For example:
\bi 
\item
For the Seigmund data,
the objective score is the runtime of the test suite of some compiled program;
\item
For the Jureczko data, the objective score
is a boolean that is true if defects have been noted
for that class.
\ei
We say that each cluster can be represented by one
{\em exemplar} that
holds independent values that best characterize that cluster:
\bi
\item
For
instances with numeric objectives (e.g. the Seigmund data), 
the exemplar of a cluster is the instance
with the best objective score.
\item
For instances with discrete objectives (e.g. Jureczko data),
there is less differentiation between the objective scores.
Hence, for this kind of the data, the exemplar of a cluster is
an instance synthesized from the median values of the instances
in that cluster.
\ei
Given the above, we can now define a {\em plan} to be
a set of values to be added to a test instance in order
to reduce the distance between that instance and the exemplar: 
\[Y_j = Y_j + f*(X_j - Y_j)\]
In the above, $Y_j$ is an independent variable within the
test instance $Y$; $X$ is the exemplar found at training time;
and  $f$ is a constant that controls
how far we  move an instance (which is tuned for different data
sets).

A core design principle for HOW was ``minimal change'';
i.e. make very small changes to the current instance.
\ei
There are many ways to find those regions 
When designing HOW, our premises were:

This is no domain model; (b)~we have some
labelled data and (b)~we seek minimal
disrupttion
HOW divide training into regions where the training
data has similar properties. Each region is then examined and divided into ``west'' and ``east''
where the region's ``west'' end has examples with worst performance stores than the east
end (mnemoc: west starts with ``w'' and is short for ``worst' and east starts with ``e;;]which is shirt
for excellent).so the ``e'' in

@@

\begin{figure}
\input{deltas1}
\caption{Jureczko data sets, experiments with tuning.}\label{fig:jtune}
\end{figure}
For the  Jureczko   object-oriented data,
the plans generated by HOW advise   how to change static code attributes in order to reduce defects in
Java classes.  Here,
performance can be measured in terms of recall (percent of faulty classes in
the test data detected
by the {\em predictor}). Using engineering judgement, we define satisfactory recall as anything over   70\%. 
This paper explores 12 of the Jureczko   object-oriented static code data sets: Ant, Camel, Ivy, Jedit, JBeans, Log4, Lucene, Poi, Synapse, Velocity, Xalan, Xerces\footnote{Available from the object-oriented defects section of the PROMISE respository openscience.us/repo/defect/ck.}.
For each of these data sets, we generated  {\em before} scores  by finding the latest
version $k$, then training  a predictor on versions $k-2$ and $k-1$. As reported below,
our initial recall scores from this data were unpromising (very low recall values). However,
after applying certain data pre-processing steps (described below), a Random Forest generated
on the $k-2,k-1$ versions achieved recalls on version $k$ of
%issue24
\[\mathrm{recall}=\{98,88,86,84,82,81,79,78,78,\overbrace{55,23,20}^{\mathrm{JBeans,Poi,Xalan}}\}\]
From the above, we conclude that all the Seigmund configuration data and most of the Jureczko data
avoids the problem of poor predictors. Hence, we can use that data for the planning
experiments described below.

@@

We reason that the most informative feature must undergo a larger change as compared to other features. Therefore, when feature weighting is employed, the higher ranked features are mutated by a larger extent. Additionally, we have also included information pruning. Here we mutate only the top X\% of the features in each test instance. The remaining features remain unaltered.
